---
title: "p8105_hw1_jf3354"
author: Judy Fordjuoh
date: September 23, 2021
output: github_document

---
###PROBLEM ONE
##Creating the dataframe

library(tidyverse) 
library(dplyr)

set.seed(10)

hw1 = tibble(
    vec_numeric = rnorm(10),
    vec_char = c("My", "name", "is", "Judy", "and", "I", "am", "learning", "data","science"),
    vec_logical = c("TRUE", "FALSE", "FALSE", "FALSE", "TRUE", "TRUE", "FALSE", "FALSE", "FALSE", "FALSE"),
    vec_factor = factor(c("low","medium","high","low","medium","high", "low","medium","high", "low"))
  )

##Take the mean of each variable in your dataframe. What works and what doesn’t?

```{r eval=FALSE}
mean(pull(hw1,vec_numeric))
mean(pull(hw1,vec_char))
mean(pull(hw1,vec_logical))
mean(pull(hw1,vec_factor))
```
## The mean of my variable vec_numeric was -0.4906568.I was not able to calculate the mean of my variables vec_char, vec_logical, and vec_factor because the argument of these variables are not numeric. 

##Convert the logical, character, and factor variables using as.numeric. What happens, and why? Does this help explain what happens when you try to take the mean?

```{r eval=FALSE} 
vf <- factor(vec_factor) ##convert vector into factor

x <- as.numeric(vf) ##convert factor into numeric value

x ##print the numeric value

is.numeric(x) ##check if this is a numeric value. If so it will print TRUE in the Console

mean(x) ##the mean is 2. 
```

```{r} 
##Logic variable 
vec_logical = c("TRUE", "FALSE", "FALSE", "FALSE", "TRUE", "TRUE", "FALSE", "FALSE", "FALSE", "FALSE")

logic <- as.numeric(factor(vec_logical))

logic

is.numeric(logic)

mean(logic) #the mean is 1.3
```

```{r} 
##Character variable 
vec_char = c("My", "name", "is", "Judy", "and", "I", "am", "learning", "data","science")

character <- as.numeric(factor(vec_char))

character

is.numeric(character)

mean(character) #the mean is 5.5
```
##

##PROBLEM 2
library(palmerpenguins)

data("penguins", package = "palmerpenguins")

```{r eval=FALSE}
data <- penguins[1:344,]
knitr::kable(data,
 caption = "Penguins Demographics")
```
